Summer 2025 ToDo

### 2025-06-18 Relations/Paper/Definitions.tex
Minor updates to the report

\apcomment{Make sure to move this stuff to Seq.agda!}
\sacomment{This will create a circular dependency as Seq is used in properties (the increasing definition is needed for BP, CP, RP, SMseq, SRv2). Simple solution is to leave RP-iffRP in implications.agda.}

% %TODO: Update below to reflect new convenion for proofs and code.
% \begin{remark}
%     It follows that every relation that is increasing in the sense of \terese $\,$ vacuously satisfies the RP condition.
% \end{remark}

@@

Our Agda formulation of the above definition makes use of the List type constructor.
\verb|FB a = Σ[ xs ∈ List A ] (∀ b → R b a → b ∈List xs)|

>>>>

@@

Our Agda formulation of the above definition makes use of the List type constructor, which we import from the \href{https://agda.github.io/agda-stdlib/v2.1/Agda.Builtin.List.html}{Agda standard library}.

\verb|FB a = Σ[ xs ∈ List A ] (∀ b → R b a → b ∈List xs)|

### 2025-06-18 Relations/Paper/Formalization.tex
Minor changes
Minor updates to the report

Most standard termination and confluence properties are defined in the file \texttt{Properties.agda}
and related files discussed in the previous seciton.  The file \texttt{Base.agda} imports all of these files
and introduces a few more notations used specifically for formalizing chapter 1 of \cite{Terese}.
\apcomment{Discuss these...}

The closure operators are formalized in \texttt{Closure.agda}.
The definitions grouped as confluent in \terese $\,$ are formalized in \texttt{Base.agda}.
The definitions grouped as normalizing in \terese $\,$ are formalized in \texttt{Properties.agda}.

@@

\begin{theorem}(Thm. 1.2.3 in [Terese])
  \begin{enumerate}[(i)]
    \item $\gWN \land \gUN \implies \gBP$
    \item $\gBP \land \gInc \implies \gSN$
    \item $\gWCR \land \gWN \land \gInc \implies \gSN$
    \item $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
  \end{enumerate}
  % \begin{description}
  %   \item[($i$)] $\gWN \land \gUN \implies \gBP$
  %   \item[($ii$)] $\gBP \land \gInc \implies \gSN$
  %   \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
  %   \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
  % \end{description}
\end{theorem}
\apcomment{Do the same for 1.2.2, and below!}

\begin{proof}
    See \texttt{Theorems.agda},\\
    \verb|i     : R isWN → R isUN → R isBP|\\
    $\mathtt{i^\to}$\hspace{5mm} \verb|: R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii   : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|\\
    \verb|iv    : R isCP → R isCR|
\end{proof}
\apcomment{Apply similar formatting elsewhere.}
\begin{proof}[Discussion.]\hfill
  \begin{description}
    \item[($i$)] In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
    \item[($ii$)] This proof is inherently classical. In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions. The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
    \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$. We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
  \end{description}
\end{proof}

>>>>

Most standard termination and confluence properties are defined in the file \texttt{Properties.agda} and related files discussed in the previous section.  The file \texttt{Base.agda} imports all of these files
and introduces a few more notations used specifically for formalizing chapter 1 of \cite{Terese}.
\apcomment{Discuss these...}

The closure operators are formalized in \texttt{ClosureOperators.agda}.
The definitions grouped as confluent in \terese $\,$ are formalized in \texttt{Base.agda}.
The definitions grouped as normalizing in \terese $\,$ are formalized in \texttt{Properties.agda}.

@@

\begin{theorem}(Thm. 1.2.3 in [Terese])
  \begin{enumerate}[(i)]
    \item $\gWN \land \gUN \implies \gBP$
    \item $\gBP \land \gInc \implies \gSN$
    \item $\gWCR \land \gWN \land \gInc \implies \gSN$
    \item $\gCR \iff \gCP$ $($the forward implication only holds if the ARS is countable.$)$
  \end{enumerate}
  % \begin{description}
  %   \item[($i$)] $\gWN \land \gUN \implies \gBP$
  %   \item[($ii$)] $\gBP \land \gInc \implies \gSN$
  %   \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
  %   \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
  % \end{description}
\end{theorem}
\apcomment{Do the same for 1.2.2, and below!}

\begin{proof}
    See \texttt{Theorems.agda},\\
    \verb|i     : R isWN → R isUN → R isBP|\\
    $\mathtt{i^\to}$\hspace{5mm} \verb|: R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii   : R isWN → R isWCR → R isRP- → dec SN → R isSN|\\
    \verb|iv    : R isCP → R isCR|
\end{proof}
\apcomment{Apply similar formatting elsewhere.}
\begin{proof}[Discussion.]\hfill
  \begin{description}
    \item[($i$)] In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
    \item[($ii$)] This proof is inherently classical. In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions. The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
    \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$. We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
  \end{description}
\end{proof}
